Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-09-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Compartment Corner Burner
Added NG and GAS images and refs.

@@

@@

\subsubsection{Natural Gas}
\subsubsection{Gasoline}
\subsubsection{Polyurethane Foam}

@@

Needed?

\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}

>>>>

Compartment experiments with the burner positioned in or near the corner were conducted with the open back wall construction.  The purpose of moving the burner position toward the corner was to examine the effect of reducing the available air entrainment area around the perimeter of the burner on the resulting fire pattern.  With the burner tight against both walls, the air entrainment perimeter was reduced by 50~\%. Previous studies on flame height with fires in corners have demonstrated the the flame height increased when compared to a similar fire positioned against a single wall or burning in the open~\cite{Poreh:1999,Saito:1993,Takahashi:1997,Kokkala:1993}.  The previous studies measured temperatures, heat flux, and mass flow rates for the purpose of developing correlations to predict flame height. The sole purpose of these experiments is to examine the fire patterns that result from well characterized fires on painted gypsum wall board.

@@

The compartment used for the corner position experiments was the same as the comapartment used for the wall positions experiments detailed in the previous section.  The burner was positioned in the left, rear corner against the face of two pieces of painted gypsum wallboard. As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment. The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.  The natural gas had a 300~s burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.  By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.  Figure~\ref{GBNG34Sequence} displays a sequence of photographs taken during a natural gas burner corner experiment.  The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.  The grid drawn on the corner extends to 1.5 m above the top of the burner.

\begin{figure}[p]
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0990}
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0991}
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0992} \\

	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0993}
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0994} 
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0995} \\

	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0996}
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0997}
	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0998} \\

	\caption[Photograph sequence of a natural gas burner positioned in a corner.]{Photograph sequence of a natural gas burner positioned in a corner. The photographs were taken 0.2 of second apart.}
	\label{GBNG34Sequence}
\end{figure}

Figure~\ref{GBGas10Sequence} displays a sequence of photographs taken during a gasoline burner corner experiment.  The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.

\begin{figure}[p]
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2046}
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2047}
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2048} \\

	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2049}
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2050} 
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2051} \\

	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2052}
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2053}
	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2054} \\

	\caption[Photograph sequence of a gasoline burner positioned in a corner.]{Photograph sequence of a gasoline burner positioned in a corner. The photographs were taken 0.2 of second apart.}
	\label{GBGas10Sequence}
\end{figure}

@@

Figure~\ref{NG_Corner} shows a comparison of the ten fire patterns generated by the natural gas burner in the corner position with walls of open back construction.

\begin{figure}[p]
	\includegraphics[width=1.0in]{../Figures/GBNG34_P5150482}
	\includegraphics[width=1.0in]{../Figures/GBNG35_IMG_9166}
	\includegraphics[width=1.0in]{../Figures/GBNG36_IMG_9181}
	\includegraphics[width=1.0in]{../Figures/GBNG37_IMG_9194}
	\includegraphics[width=1.0in]{../Figures/GBNG38_IMG_9208} \\

	\includegraphics[width=1.0in]{../Figures/GBNG39_IMG_9222}
	\includegraphics[width=1.0in]{../Figures/GBNG40_IMG_9235}
	\includegraphics[width=1.0in]{../Figures/GBNG41_IMG_9249}
	\includegraphics[width=1.0in]{../Figures/GBNG42_IMG_9262}
	\includegraphics[width=1.0in]{../Figures/GBNG43_IMG_9275} \\

	\caption[Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner]{Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner.}
	\label{NG_Corner}
\end{figure}

\subsubsection{Gasoline}
\subsubsection{Polyurethane Foam}

@@

Needed?
{}
\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}
